### 2022-07-15 chapters/interpretability/relaxed-cnf/experiment.tex
notations updated
considering all minor comments

\section{Experiments}\label{interpretability_crr_sec:experiment}
We implement a prototype  of  the incremental version of $ \crr $\footnote{The source code is available at \url{https://github.com/meelgroup/mlic}} based on the  Python API for CPLEX  and conduct an extensive  empirical analysis to understand the behavior of $\crr$ on real-world instances. The objective of our experimental evaluation is to answer the following questions:

@@

	\caption[Accuracy, rule-size, and training time of rule-based classifiers]{Comparisons of test accuracy, rule-size and training time among different rule-based classifiers. Every cell in the last four columns contains the test accuracy in percentage (top value), rule size  (middle value), and  training time in seconds (bottom value). In the experiments, {\crr} shows higher test accuracy than IMLI and generates sparser rules than RIPPER.}

@@

	\setlength{\tabcolsep}{3pt} 

@@

			{ Heart}   & $  303 $  & $  31 $  & $   78.69  $    & $   72.13  $    & $   72.13  $    & $   77.69  $   \\[0.05cm] & & 
			& $   7 $    & $   19 $    & $   13 $    & $   4.5  $   \\[0.05cm] & & 
			& $   5.27 \text{s}  $    & $   25.07 \text{s}  $    & $   1.8 \text{s}  $    & $   122.5 \text{s}  $   \\[.3cm] 
			{ Ionosphere}   & $  351 $  & $  144 $  & $   88.65  $    & $   91.43  $    & $   89.29  $    & $   91.43  $   \\[0.05cm] & & 
			& $   8 $    & $   4 $    & $   8.5  $    & $   20 $   \\[0.05cm] & & 
			& $   5.87 \text{s}  $    & $   75.53 \text{s}  $    & $   2.09 \text{s}  $    & $   5.59 \text{s}  $   \\[.3cm] 
			{ WDBC}   & $  569 $  & $  88 $  & $   95.22  $    & $   95.65  $    & $   93.91  $    & $   94.69  $   \\[0.05cm] & & 
			& $   7.5  $    & $   12 $    & $   7 $    & $   34.5  $   \\[0.05cm] & & 
			& $   5.7 \text{s}  $    & $   630.23 \text{s}  $    & $   1.38 \text{s}  $    & $   316.32 \text{s}  $   \\[.3cm] 
			{ Magic}   & $  19020 $  & $  79 $  & $   84.04  $    & $   74.15  $    & $   71.97  $    & $   81.31  $   \\[0.05cm] & & 
			& $   115 $    & $   3 $    & $   24 $    & $   31 $   \\[0.05cm] & & 
			& $   15.86 \text{s}  $    & $   56.46 \text{s}  $    & $   141.2 \text{s}  $    & $   1012.6 \text{s}  $   \\[.3cm] 
			{ Tom's HW}   & $  28179 $  & $  910 $  & $   97.4  $    &   \multicolumn{1}{c}{\multirow{3}{*}{\textemdash}}       & $   95.88  $    & $   97.34  $   \\[0.05cm] & & 
			& $   36 $    &       & $   30 $    & $   4 $   \\[0.05cm] & & 
			& $   42.73 \text{s}  $    &       & $   92.65 \text{s}  $    & $   1071.58 \text{s}  $   \\[.3cm] 
			{ Credit}   & $  30000 $  & $  110 $  & $   81.68  $    &   \multicolumn{1}{c}{\multirow{3}{*}{\textemdash}}       & $   81.42  $    & $   82.04  $   \\[0.05cm] & & 
			& $   38.5  $    &       & $   10 $    & $   32 $   \\[0.05cm] & & 
			& $   14.52 \text{s}  $    &       & $   17.66 \text{s}  $    & $   1021.35 \text{s}  $   \\[.3cm] 
			{ Adult}   & $  32561 $  & $  144 $  & $   84.31  $    &   \multicolumn{1}{c}{\multirow{3}{*}{\textemdash}}       & $   82.08  $    & $   84.86  $   \\[0.05cm] & & 
			& $   94 $    &       & $   23 $    & $   18 $   \\[0.05cm] & & 
			& $   27.61 \text{s}  $    &       & $   11.91 \text{s}  $    & $   1016.36 \text{s}  $   \\[.3cm] 
			{ Twitter}   & $  49999 $  & $  1511 $  & $   95.74  $    &   \multicolumn{1}{c}{\multirow{3}{*}{\textemdash}}       & $   94.24  $    & $   95.16  $   \\[0.05cm] & & 
			& $   179.5  $    &       & $   57 $    & $   12 $   \\[0.05cm] & & 
			& $   170.87 \text{s}  $    &       & $   238.29 \text{s}  $    & $   1144.66 \text{s}  $   \\[.3cm] 
			{ Weather-AUS}   & $  107696 $  & $  141 $  & $   84.57  $    &   \multicolumn{1}{c}{\multirow{3}{*}{\textemdash}}       & $   82.83  $    & $   83.34  $   \\[0.05cm] & & 
			& $   195 $    &       & $   7 $    & $   2 $   \\[0.05cm] & & 
			& $   121.02 \text{s}  $    &       & $   366.12 \text{s}  $    & $   1115.27 \text{s}  $   \\[.3cm] 
			{ Skin}   & $  245057 $  & $  119 $  & $   98.32  $    &   \multicolumn{1}{c}{\multirow{3}{*}{\textemdash}}       & $   98.92  $    & $   95.08  $   \\[0.05cm] & & 
			& $   725 $    &       & $   201 $    & $   29 $   \\[0.05cm] & & 
			& $   1313.19 \text{s}  $    &       & $   103.8 \text{s}  $    & $   825.6 \text{s}  $   \\[.3cm] 

@@

We consider a comparable number  of hyper-parameter choices  for each classifier. Specifically for {\crr}, we choose the data-fidelity parameter $ \lambda \in \{0.5, 0.67, 0.84, 0.99\} $, the number of clauses $ k \in \{1,2,3\} $, the relative size of mini-batch $ \frac{n_p}{n} \in \{0.25, 0.50, 0.75\} $, and the number of iterations $ \tau \in \{2,4,8,16\} $. We learn the value of $ \card_c $ and $ \eta_{l} $ from the dataset as described in Eq.~\ref{interpretability_crr_sec:ilp_query}.  In CPLEX, we set the  maximum solving time of the LP solver to $ 1000 $  seconds ($ \frac{ 1000 }{\tau} $ seconds for each iteration) and the remaining $ 500 $ seconds is allotted to construct the MLIP instances, parse the solutions and execute  other auxiliary tasks of the learning algorithm. We present the current best solution of CPLEX when the solver times out while finding the optimal solution.

@@

We first compare relaxed-CNF rules generated by {\crr} with CNF rules generated by IMLI. In {Table}~\ref{interpretability_crr_tab:rule_based_classifiers}, relaxed-CNF rules exhibit higher prediction accuracy than CNF rules in the majority of the datasets, showing the effectiveness of using a more expressive representation of classification rules in capturing the decision boundary. In addition, the generated relaxed-CNF rules are comparatively smaller than CNF rules in terms of rule-size in most of the datasets. Therefore, relaxed-CNF rules improve upon CNF rules in terms of both prediction accuracy and rule size in the majority of the datasets. In this context, {\crr} provides a trade-off between accuracy and rule-size depending on the choice of hyper-parameters and the experimental results are discussed later in Section~\ref{interpretability_crr_sec:model_parameters}.  We then compare relaxed-CNF rules with DNF rules generated by BRS and find that relaxed-CNF rules outperform DNF rules with respect to prediction accuracy in several datasets. At this point,   BRS fails to scale for larger datasets as shown in Table~\ref{interpretability_crr_tab:rule_based_classifiers}. We finally compare relaxed-CNF rules with decision lists generated by RIPPER.  In the experiments, relaxed-CNF rules achieve comparable prediction accuracy with decision lists in most of the datasets. In contrast,   RIPPER generates very large decision lists compared to relaxed-CNF rules in the majority of the datasets, more precisely in large datasets.  To summarize the performance of {\crr} among different rule-based classifiers,  {\crr} can generate smaller relaxed-CNF rules with better accuracy in numbers of the cases with a couple of exceptions.

@@

\begin{table}
	\caption[Accuracy of {\crr} and non-rule-based classifiers]{Comparisons of test accuracy among {\crr} and  non-rule-based classifiers. In the experiments, {\crr} achieves competitive prediction accuracy in spite of being a rule-based classifier.}
	\label{interpretability_crr_tab:all_classifiers}
	\begin{center}
		\begin{tabular}{l   r r r r r  r }
			\toprule
			{Dataset}  & LR & SVC & RF & $k$-NN & CRR\\\midrule
			\multirow{1}{*}{ Heart}   & $   84.29  $    & $   83.33  $    & $   81.97  $    & $   78.69  $    & $   77.69  $   \\ 
			\multirow{1}{*}{ Ionosphere}   & $   94.29  $    & $   91.43  $    & $   92.96  $    & $   91.43  $    & $   91.43  $   \\ 
			\multirow{1}{*}{ WDBC}   & $   98.26  $    & $   96.46  $    & $   96.9  $    & $   95.61  $    & $   94.69  $   \\ 
			\multirow{1}{*}{ Magic}   & $   85.15  $    & $   84.45  $    & $   85.3  $    & $   77.9  $    & $   81.31  $   \\ 
			\multirow{1}{*}{ Tom's HW}   & $   97.62  $    & $   97.66  $    & $   97.52  $    & $   94.59  $    & $   97.34  $   \\ 
			\multirow{1}{*}{ Credit}   & $   82.04  $    & $   82.12  $    & $   81.97  $    & $   80.5  $    & $   82.04  $   \\ 
			\multirow{1}{*}{ Adult}   & $   87.24  $    & $   86.82  $    & $   86.84  $    & $   84.68  $    & $   84.86  $   \\ 
			\multirow{1}{*}{ Twitter}   & $   96.28  $    & $   96.34  $    & $   96.37  $     &  \multicolumn{1}{c}{\textemdash}      & $   95.16  $   \\ 
			\multirow{1}{*}{ Weather-AUS}   & $   85.71  $     &  \multicolumn{1}{c}{\textemdash}      & $   85.63  $     &  \multicolumn{1}{c}{\textemdash}      & $   83.34  $   \\ 
			\multirow{1}{*}{ Skin}   & $   97.21  $     &  \multicolumn{1}{c}{\textemdash}      & $   99.81  $     &  \multicolumn{1}{c}{\textemdash}      & $   95.08  $   \\ 
			\bottomrule
		\end{tabular}
	\end{center}
\end{table}

\begin{figure}[t]
	%%\vspace{-25pt}
	\centering
	\subfloat
	{\includegraphics[width=0.23\textwidth]{figures/interpretability/relaxed-cnf/heart_test_accuracy_vary_lambda.pdf}\label{interpretability_crr_fig:d}} \hfill
	\subfloat
	{\includegraphics[width=0.23\textwidth]{figures/interpretability/relaxed-cnf/heart_test_accuracy_vary_clause.pdf}\label{interpretability_crr_fig:f}} \hfill
	\subfloat
	{\includegraphics[width=0.23\textwidth]{figures/interpretability/relaxed-cnf/heart_test_accuracy_vary_subsamplesize.pdf}
		\label{interpretability_crr_fig:a}} \hfill
	\subfloat
	{\includegraphics[width=0.23\textwidth]{figures/interpretability/relaxed-cnf/heart_test_accuracy_vary_iteration.pdf}\label{interpretability_crr_fig:g}} \hfill
	\caption[Effect of hyper-parameters on accuracy in {\crr}]{Effect of model hyper-parameters on test accuracy  for  Heart disease dataset. } 
	\label{interpretability_crr_fig:result_1}
\end{figure}

%%\vspace{-3pt}
	\subsubsection*{Varying Model Parameters: }
	\label{interpretability_crr_sec:model_parameters}
	In Figure~\ref{interpretability_crr_fig:result_1},~\ref{interpretability_crr_fig:result_2}, and~\ref{interpretability_crr_fig:result_3}, we demonstrate the effect of varying the hyper-parameters of {\crr}. To understand the effect of a single hyper-parameter, we fix the values of other hyper-parameters to a default choice where the default choice results in the most accurate rule.

	%	%%\vspace{-3pt}
	\textbf{Varying data-fidelity parameter ($ \lambda $):}  As we increase data-fidelity parameter $ \lambda $ in the objective function in Eq.~\ref{interpretability_crr_eq:ilp_obj} and Eq.~\ref{interpretability_crr_eq:ilp_inc}, more priority is given to the prediction accuracy than the sparsity of the rules.  In most of the datasets, we similarly observe an increase in accuracy  and also an increase in the size of the rules when $ \lambda $ is higher. This suggests that improved interpretability can often come at a  minor cost in accuracy.  
	In addition, we  find an increase in training time for most of the datasets indicating that the MILP query usually takes a longer time to find the solution when more priority is given on the prediction accuracy.

	\begin{figure}[t]
		%%\vspace{-25pt}
		\centering
		\subfloat
		{\includegraphics[width=0.23\textwidth]{figures/interpretability/relaxed-cnf/heart_rule_size_vary_lambda.pdf}\label{interpretability_crr_fig:c}} \hfill
		\subfloat
		{\includegraphics[width=0.23\textwidth]{figures/interpretability/relaxed-cnf/heart_rule_size_vary_clause.pdf}\label{interpretability_crr_fig:h}} \hfill
		\subfloat
		{\includegraphics[width=0.23\textwidth]{figures/interpretability/relaxed-cnf/heart_rule_size_vary_subsamplesize.pdf}\label{interpretability_crr_fig:b}} \hfill 
		\subfloat
		{\includegraphics[width=0.23\textwidth]{figures/interpretability/relaxed-cnf/heart_rule_size_vary_iteration.pdf}\label{interpretability_crr_fig:e}} \hfill
		%%\vspace{-10pt}
		\caption[Effect of hyper-parameters on rule-size in {\crr}]{Effect of model hyper-parameters on rule-size for  Heart disease dataset.}

		%\vspace{-10pt}
		\label{interpretability_crr_fig:result_2}
	\end{figure}

	{\textbf{Varying the number of clauses ($ k $): }}
	%	In Figure~\ref{interpretability_crr_fig:clause(a)}, we show the effect of $ k $ on  test accuracy   for Parkinsons {dataset}. 
	As we increase  $ k $, {\crr} allows the generated rules to capture the variance in the given dataset more effectively, that results in higher  accuracy in most of the datasets. The  rule-size also increases as we learn more clauses. In addition, the training time  increases, that can be reasoned by the fact that the number of constraints in the MILP formulation is linear with $ k $. Thereby, the number of clauses $ k $ provides a control over the accuracy of the generated rule and training time.

	 \begin{figure}[btp]
	 	%%\vspace{-25pt}
	 	\centering
	 	\subfloat
	 	{\includegraphics[width=0.23\textwidth]{figures/interpretability/relaxed-cnf/heart_time_vary_lambda.pdf}\label{interpretability_crr_fig:c}} \hfill
	 	\subfloat
	 	{\includegraphics[width=0.23\textwidth]{figures/interpretability/relaxed-cnf/heart_time_vary_clause.pdf}\label{interpretability_crr_fig:h}} \hfill
	 		\subfloat
	 		{\includegraphics[width=0.23\textwidth]{figures/interpretability/relaxed-cnf/heart_time_vary_subsamplesize.pdf}\label{interpretability_crr_fig:b}} \hfill 
	 		\subfloat
	 		{\includegraphics[width=0.23\textwidth]{figures/interpretability/relaxed-cnf/heart_time_vary_iteration.pdf}\label{interpretability_crr_fig:e}} \hfill
	 	%	%%\vspace{-10pt}
	 	\caption[Effect of hyper-parameters on training time in {\crr}]{Effect of model hyper-parameters on training  time for  Heart disease dataset.}

	 	%\vspace{-10pt}
	 	\label{interpretability_crr_fig:result_3}
	 \end{figure}

	\textbf{Relative size of the mini-batch:} We vary the relative size of the mini-batch $ \frac{n_p}{n} $ to observe its effect on the accuracy and the size of the rules. In most datasets,  the accuracy increases when more samples are considered in the mini-batch, costing higher   training time.  Moreover, the size of the generated rule increases as $ \frac{n_p}{n} $ increases, that can be supported by the increase  in the variance of the samples in the mini-batch.

	%	%%\vspace{-3pt}
	\textbf{Varying the number of iterations ($ \tau $):}   
	As we allow more iterations in the learning process, we find an increase in accuracy in most datasets. The training time also increases with $ \tau $ because {\crr} is required to solve in total $ \tau $ queries. We also observe an increase in rule-size in most datasets. The reason is that the objective function in the incremental mini-batch approach in Eq.~\ref{interpretability_crr_eq:ilp_inc} does not put a restriction on the size of the rules, rather on the change of rules in consecutive iterations.  In addition, the learned values of the thresholds $ \eta_c$ and $ \eta_l $  in one iteration are not carried to the MILP query in the next iteration, that may cause an increase of rule-size.

>>>>

\section{Experiments}\label{interpretability_crr_sec:experiment}
We implement a prototype  of  $ \crr $\footnote{The source code is available at \url{https://github.com/meelgroup/mlic}} based on the  Python API for CPLEX  and conduct an extensive  empirical analysis to understand the behavior of $\crr$ on real-world instances. The objective of our experimental evaluation is to answer the following questions:

@@

	\caption[Accuracy, rule-size, and training time of rule-based classifiers]{Comparisons of test accuracy, rule-size and training time among different rule-based classifiers. Every cell in the last four columns contains the test accuracy in percentage (top value), rule size  (middle value), and  training time in seconds (bottom value). In the experiments, {\crr} shows higher test accuracy than IMLI and generates sparser rules than RIPPER. Number in bold denotes the best result, such as maximum test accuracy, minimum rule-size, and minimum training time among competitive classifiers.}

@@

%	\setlength{\tabcolsep}{3pt} 

@@

			{ Heart}   & $  303 $  & $  31 $  & $   \textbf{78.69}  $    & $   72.13  $    & $   72.13  $    & $   77.69  $   \\ & & 
			& $   7 $    & $   19 $    & $   13 $    & $   \textbf{4.5}  $   \\ & & 
			& $   5.27 \text{s}  $    & $   25.07 \text{s}  $    & $   \textbf{1.8} \text{s}  $    & $   122.5 \text{s}  $   \\\\
			{ Ionosphere}   & $  351 $  & $  144 $  & $   88.65  $    & $   \textbf{91.43}  $    & $   89.29  $    & $   \textbf{91.43}  $   \\ & & 
			& $   8 $    & $   \textbf{4} $    & $   8.5  $    & $   20 $   \\ & & 
			& $   5.87 \text{s}  $    & $   75.53 \text{s}  $    & $   \textbf{2.09} \text{s}  $    & $   5.59 \text{s}  $   \\\\ 
			{ WDBC}   & $  569 $  & $  88 $  & $   95.22  $    & $   \textbf{95.65}  $    & $   93.91  $    & $   94.69  $   \\ & & 
			& $   7.5  $    & $   12 $    & $   \textbf{7} $    & $   34.5  $   \\ & & 
			& $   5.7 \text{s}  $    & $   630.23 \text{s}  $    & $   \textbf{1.38} \text{s}  $    & $   316.32 \text{s}  $   \\\\ 
			{ Magic}   & $  19020 $  & $  79 $  & $   \textbf{84.04}  $    & $   74.15  $    & $   71.97  $    & $   81.31  $   \\ & & 
			& $   115 $    & $   \textbf{3} $    & $   24 $    & $   31 $   \\ & & 
			& $   \textbf{15.86} \text{s}  $    & $   56.46 \text{s}  $    & $   141.2 \text{s}  $    & $   1012.6 \text{s}  $   \\\\ 
			{ Tom's HW}   & $  28179 $  & $  910 $  & $   \textbf{97.4}  $    &   \multicolumn{1}{c}{\multirow{3}{*}{\textemdash}}       & $   95.88  $    & $   97.34  $   \\ & & 
			& $   36 $    &       & $   30 $    & $   \textbf{4} $   \\ & & 
			& $   \textbf{42.73} \text{s}  $    &       & $   92.65 \text{s}  $    & $   1071.58 \text{s}  $   \\\\ 
			{ Credit}   & $  30000 $  & $  110 $  & $   81.68  $    &   \multicolumn{1}{c}{\multirow{3}{*}{\textemdash}}       & $   81.42  $    & $  \textbf{ 82.04}  $   \\ & & 
			& $   38.5  $    &       & $   \textbf{10} $    & $   32 $   \\ & & 
			& $   \textbf{14.52} \text{s}  $    &       & $   17.66 \text{s}  $    & $   1021.35 \text{s}  $   \\\\ 
			{ Adult}   & $  32561 $  & $  144 $  & $   84.31  $    &   \multicolumn{1}{c}{\multirow{3}{*}{\textemdash}}       & $   82.08  $    & $   \textbf{84.86}  $   \\ & & 
			& $   94 $    &       & $   23 $    & $   \textbf{18} $   \\ & & 
			& $   27.61 \text{s}  $    &       & $   \textbf{11.91} \text{s}  $    & $   1016.36 \text{s}  $   \\\\ 
			{ Twitter}   & $  49999 $  & $  1511 $  & $   \textbf{95.74}  $    &   \multicolumn{1}{c}{\multirow{3}{*}{\textemdash}}       & $   94.24  $    & $   95.16  $   \\ & & 
			& $   179.5  $    &       & $   57 $    & $   \textbf{12} $   \\ & & 
			& $   \textbf{170.87} \text{s}  $    &       & $   238.29 \text{s}  $    & $   1144.66 \text{s}  $   \\\\ 
			{ Weather-AUS}   & $  107696 $  & $  141 $  & $   \textbf{84.57}  $    &   \multicolumn{1}{c}{\multirow{3}{*}{\textemdash}}       & $   82.83  $    & $   83.34  $   \\ & & 
			& $   195 $    &       & $   7 $    & $   \textbf{2} $   \\ & & 
			& $   \textbf{121.02} \text{s}  $    &       & $   366.12 \text{s}  $    & $   1115.27 \text{s}  $   \\\\ 
			{ Skin}   & $  245057 $  & $  119 $  & $   98.32  $    &   \multicolumn{1}{c}{\multirow{3}{*}{\textemdash}}       & $   \textbf{98.92}  $    & $   95.08  $   \\ & & 
			& $   725 $    &       & $   201 $    & $   \textbf{29} $   \\ & & 
			& $   1313.19 \text{s}  $    &       & $   \textbf{103.8} \text{s}  $    & $   825.6 \text{s}  $   \\\\ 

@@

We consider a comparable number  of hyper-parameter choices  for each classifier. Specifically for {\crr}, we choose the data-fidelity parameter $ \lambda \in \{0.5, 0.67, 0.84, 0.99\} $, the number of clauses $ k \in \{1,2,3\} $, the relative size of mini-batch $ \frac{n_p}{n} \in \{0.25, 0.50, 0.75\} $, and the number of iterations $ \tau \in \{2,4,8,16\} $. We learn the value of $ \card_c $ and $ \eta_{l} $ from the dataset as described in Chapter.~\ref{interpretability_crr_sec:ilp_query}.  In CPLEX, we set the  maximum solving time of the LP solver to $ 1000 $  seconds ($ \frac{ 1000 }{\tau} $ seconds for each iteration) and the remaining $ 500 $ seconds is allotted to construct the MLIP instances, parse the solutions and execute  other auxiliary tasks of the learning algorithm. We present the current best solution of CPLEX when the solver times out while finding the optimal solution.

@@

We first compare relaxed-CNF rules generated by {\crr} with CNF rules generated by IMLI. In {Table}~\ref{interpretability_crr_tab:rule_based_classifiers}, relaxed-CNF rules exhibit higher prediction accuracy than CNF rules in the majority of the datasets, showing the effectiveness of using a more expressive representation of classification rules in capturing the decision boundary. In addition, the generated relaxed-CNF rules are comparatively smaller than CNF rules in terms of rule-size in most of the datasets. Therefore, relaxed-CNF rules improve upon CNF rules in terms of both prediction accuracy and rule size in the majority of the datasets. In this context, {\crr} provides a trade-off between accuracy and rule-size depending on the choice of hyper-parameters and the experimental results are discussed later in Section~\ref{interpretability_crr_sec:model_parameters}.  We then compare relaxed-CNF rules with DNF rules generated by BRS and find that relaxed-CNF rules outperform DNF rules with respect to prediction accuracy in several datasets. At this point,   BRS fails to scale on larger datasets as shown in Table~\ref{interpretability_crr_tab:rule_based_classifiers}. We finally compare relaxed-CNF rules with decision lists generated by RIPPER.  In the experiments, relaxed-CNF rules achieve comparable prediction accuracy with decision lists in most of the datasets. In contrast,   RIPPER generates very large decision lists compared to relaxed-CNF rules in the majority of the datasets, more precisely in large datasets.  To summarize the performance of {\crr} among different rule-based classifiers,  {\crr} can generate smaller relaxed-CNF rules with better accuracy in numbers of the cases with a couple of exceptions.

@@

\begin{table}
	\caption[Accuracy of {\crr} and non-rule-based classifiers]{Comparisons of test accuracy among {\crr} and  non-rule-based classifiers. In the experiments, {\crr} achieves competitive prediction accuracy in spite of being a rule-based classifier.}
	\label{interpretability_crr_tab:all_classifiers}
	\begin{center}
		\begin{tabular}{l   r r r r r  r }
			\toprule
			{Dataset}  & LR & SVC & RF & $k$-NN & CRR\\\midrule
			\multirow{1}{*}{ Heart}   & $   \textbf{84.29}  $    & $   83.33  $    & $   81.97  $    & $   78.69  $    & $   77.69  $   \\ 
			\multirow{1}{*}{ Ionosphere}   & $   \textbf{94.29}  $    & $   91.43  $    & $   92.96  $    & $   91.43  $    & $   91.43  $   \\ 
			\multirow{1}{*}{ WDBC}   & $   \textbf{98.26}  $    & $   96.46  $    & $   96.90  $    & $   95.61  $    & $   94.69  $   \\ 
			\multirow{1}{*}{ Magic}   & $   85.15  $    & $   84.45  $    & $   \textbf{85.30}  $    & $   77.9  $    & $   81.31  $   \\ 
			\multirow{1}{*}{ Tom's HW}   & $   97.62  $    & $   \textbf{97.66}  $    & $   97.52  $    & $   94.59  $    & $   97.34  $   \\ 
			\multirow{1}{*}{ Credit}   & $   82.04  $    & $   \textbf{82.12}  $    & $   81.97  $    & $   80.5  $    & $   82.04  $   \\ 
			\multirow{1}{*}{ Adult}   & $   \textbf{87.24}  $    & $   86.82  $    & $   86.84  $    & $   84.68  $    & $   84.86  $   \\ 
			\multirow{1}{*}{ Twitter}   & $   96.28  $    & $   96.34  $    & $   \textbf{96.37}  $     &  \multicolumn{1}{c}{\textemdash}      & $   95.16  $   \\ 
			\multirow{1}{*}{ Weather-AUS}   & $   \textbf{85.71}  $     &  \multicolumn{1}{c}{\textemdash}      & $   85.63  $     &  \multicolumn{1}{c}{\textemdash}      & $   83.34  $   \\ 
			\multirow{1}{*}{ Skin}   & $   97.21  $     &  \multicolumn{1}{c}{\textemdash}      & $   \textbf{99.81}  $     &  \multicolumn{1}{c}{\textemdash}      & $   95.08  $   \\ 
			\bottomrule
		\end{tabular}
	\end{center}
\end{table}

\begin{figure}[t]
	\centering

	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/heart_test_accuracy_vary_lambda.pdf}}
	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/heart_rule_size_vary_lambda.pdf}}
	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/heart_time_vary_lambda.pdf}} 
	\\

	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/wdbc_test_accuracy_vary_lambda.pdf}}
	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/wdbc_rule_size_vary_lambda.pdf}}
	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/wdbc_time_vary_lambda.pdf}} 
	\\

	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/adult_test_accuracy_vary_lambda.pdf}}
	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/adult_rule_size_vary_lambda.pdf}}
	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/adult_time_vary_lambda.pdf}} 
	\\

	\caption[Effect of data-fidelity $ \lambda $ in {\crr}]{Effect of data-fidelity $ \lambda $ on test accuracy, rule-size, and training time in {\crr}. } 
	\label{interpretability_crr_fig:result_lambda}
\end{figure}

\begin{figure}[t]
	\centering

	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/heart_test_accuracy_vary_clause.pdf}}
	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/heart_rule_size_vary_clause.pdf}}
	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/heart_time_vary_clause.pdf}} 
	\\

	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/wdbc_test_accuracy_vary_clause.pdf}}
	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/wdbc_rule_size_vary_clause.pdf}}
	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/wdbc_time_vary_clause.pdf}} 
	\\

	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/adult_test_accuracy_vary_clause.pdf}}
	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/adult_rule_size_vary_clause.pdf}}
	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/adult_time_vary_clause.pdf}} 
	\\

	\caption[Effect of the number of clause $ k $ in {\crr}]{Effect of the number of clause $ k $ on test accuracy, rule-size, and training time in {\crr}. } 
	\label{interpretability_crr_fig:result_clause}
\end{figure}

\begin{figure}[t]
	\centering

	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/heart_test_accuracy_vary_subsamplesize.pdf}}
	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/heart_rule_size_vary_subsamplesize.pdf}}
	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/heart_time_vary_subsamplesize.pdf}} 
	\\

	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/wdbc_test_accuracy_vary_subsamplesize.pdf}}
	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/wdbc_rule_size_vary_subsamplesize.pdf}}
	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/wdbc_time_vary_subsamplesize.pdf}} 
	\\

	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/adult_test_accuracy_vary_subsamplesize.pdf}}
	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/adult_rule_size_vary_subsamplesize.pdf}}
	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/adult_time_vary_subsamplesize.pdf}} 
	\\

	\caption[Effect of mini-batch size in {\crr}]{Effect of mini-batch size on test accuracy, rule-size, and training time in {\crr}. } 
	\label{interpretability_crr_fig:result_minibatch}
\end{figure}

\begin{figure}[t]
	\centering

	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/heart_test_accuracy_vary_iteration.pdf}}
	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/heart_rule_size_vary_iteration.pdf}}
	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/heart_time_vary_iteration.pdf}} 
	\\

	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/wdbc_test_accuracy_vary_iteration.pdf}}
	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/wdbc_rule_size_vary_iteration.pdf}}
	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/wdbc_time_vary_iteration.pdf}} 
	\\

	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/adult_test_accuracy_vary_iteration.pdf}}
	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/adult_rule_size_vary_iteration.pdf}}
	\subfloat
	{\includegraphics[width=0.27\textwidth]{figures/interpretability/relaxed-cnf/adult_time_vary_iteration.pdf}} 
	\\

	\caption[Effect of the number of iterations in {\crr}]{Effect of the number of iterations on test accuracy, rule-size, and training time in {\crr}. } 
	\label{interpretability_crr_fig:result_iteration}
\end{figure}

	\subsubsection*{Varying Model Parameters: }
	\label{interpretability_crr_sec:model_parameters}
	In Figure~\ref{interpretability_crr_fig:result_lambda},~\ref{interpretability_crr_fig:result_clause}, ,~\ref{interpretability_crr_fig:result_minibatch}, and~\ref{interpretability_crr_fig:result_iteration}, we demonstrate the effect of varying the hyper-parameters of {\crr}. To understand the effect of a single hyper-parameter, we fix the values of other hyper-parameters to a default choice where the default choice results in the most accurate rule.

	\paragraph{Varying data-fidelity parameter ($ \lambda $):} In Figure~\ref{interpretability_crr_fig:result_lambda}, as we increase data-fidelity parameter $ \lambda $ in the objective function in Eq.~\ref{interpretability_crr_eq:ilp_obj} and Eq.~\ref{interpretability_crr_eq:ilp_inc}, more priority is given to the prediction accuracy than the sparsity of the rules.  In most of the datasets, we similarly observe an increase in accuracy  and also an increase in the size of the rules when $ \lambda $ is higher. This suggests that improved interpretability can often come at a  minor cost in accuracy.  In addition, we  find an increase in training time for most of the datasets indicating that the MILP query usually takes a longer time to find the solution when more priority is given on the prediction accuracy.

	\paragraph{Varying the number of clauses ($ k $): }
	In Figure~\ref{interpretability_crr_fig:result_clause}, as we increase  $ k $, {\crr} allows the generated rules to capture the variance in the given dataset more effectively, that results in higher  accuracy in most of the datasets. The  rule-size also increases as we learn more clauses. In addition, the training time  increases, that can be reasoned by the fact that the number of constraints in the MILP formulation is linear with $ k $. Thereby, the number of clauses $ k $ provides a control over the accuracy of the generated rule and training time.
